---
title: EJMap Metadata, Selected Variables, and Column Names
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
urlcolor: blue
params:
  title: NULL
  epa_funding: NULL
  df_metrics: NULL
  df_cats: NULL
  df_sources: NULL
  percentile_type: NULL
  min_percentile: 80
  min_score: 0
  min_pass: 4
  always_allow_html: true
---

```{r setup, echo = FALSE, message = FALSE}
# Import packages
library(kableExtra)
library(dplyr)
```

# File Metadata

## Title
`r params$title`

## Description
Environmental justice indicators and priority areas in the Narragansett Bay 
region at the U.S. Census "block group" scale. Scores were calculated using 
the Narragansett Bay Estuary Program (NBEP) 
[**EJMAP**](https://nbep.shinyapps.io/ejmap/) tool. This dataset is intended 
for general planning, graphic display, and GIS analysis.

## Data Source
```{r text_dataSource, echo = FALSE, results = 'asis'}

# Summarize data source, source year for selected indicators
df_dataSource <- params$df_metrics %>%
  # Select data source, source year columns; sort by year
  select(DATA_SOURCE, SOURCE_YEAR) %>%
  arrange(SOURCE_YEAR) %>%
  # Drop duplicate rows
  unique() %>%
  # Group data by data source, concatenate source year
  group_by(DATA_SOURCE) %>%
  summarize(SOURCE_YEAR = toString(SOURCE_YEAR))

# Summarize data source, source year for block groups
df_nbep <- params$df_sources %>%
  filter(DATA_SOURCE == 'NBEP')

# Combine datasets
df_dataSource <- df_dataSource %>%
    add_row(DATA_SOURCE = 'NBEP', 
            SOURCE_YEAR = toString(df_nbep$SOURCE_YEAR))

# Import list of name substitutions 
df_sources <- params$df_sources %>%
  select(DATA_SOURCE, DATA_SOURCE_LONG)

# Join datasets, add column with concatenated data source, source year
df_source <- left_join(x=df_dataSource, y=df_sources, by='DATA_SOURCE') %>%
  mutate(DATA_SOURCE_LONG = ifelse(is.na(DATA_SOURCE_LONG), 
                                   DATA_SOURCE, 
                                   DATA_SOURCE_LONG)) %>%
  # Add new column that concatenates data source, source year
  mutate(DATA_SUMMARY = paste0(DATA_SOURCE_LONG, ' (', SOURCE_YEAR, ')'))

list_dataSource <- paste(df_source$DATA_SUMMARY, collapse = '; ')

cat(list_dataSource)

```

## Date Published
`r Sys.Date()`

## Use Limitations
```{r text_limitations, echo = FALSE, results = 'asis'}
lim_string <- '<p>This dataset is provided "as is". The producer(s) of this 
  dataset, contributors to this dataset, and the Narragansett Bay Estuary 
  Program (NBEP) do not make any warranties of any kind for this dataset, and 
  are not liable for any loss or damage however and whenever caused by any use 
  of this dataset.'

# Check if First Street in list
if (grepl('First Street', list_dataSource, fixed=TRUE)){
  lim_string <- paste(lim_string, 'This data is provided under the 
    [**Attribution-NonCommercial-ShareAlike 4.0 International (CC BY-NC-SA 4.0) 
    license**](https://creativecommons.org/licenses/by-nc-sa/4.0/).')
  
} else {
  lim_string <- paste(lim_string, 'There are no restrictions or legal 
  prerequisites for using the data.')
}

lim_string <- paste(
  lim_string, 'Once acquired, any modification made to the data must be noted 
  in the metadata. Please acknowledge both NBEP and the primary producer(s) of 
  this dataset or any derived products.</p><p>These data are intended for use as a 
  tool for reference, display, and general GIS analysis purposes only. It is the 
  responsibility of the data user to use the data appropriately and consistent 
  with the limitations of geospatial data in general and these data in 
  particular. The information contained in these data may be dynamic and could 
  change over time. The data accuracy is checked against best available sources 
  which may be dated. The data are not better than the original sources from 
  which they are derived. These data are not designed for use as a primary 
  regulatory tool in permitting or siting decisions and are not a legally 
  authoritative source for the location of natural or manmade features. The 
  depicted boundaries, interpretations, and analysis derived from them have not 
  been verified at the site level and do not eliminate the need for onsite 
  sampling, testing, and detailed study of specific sites.</p><p>This project was 
  funded by agreements by the Environmental Protection Agency (EPA) to Roger 
  Williams University (RWU) in partnership with the Narragansett Bay Estuary 
  Program. Although the information in this document has been funded wholly or 
  in part by EPA under the agreements', params$epa_funding, 'to RWU, it has not 
  undergone the Agency’s publications review process and therefore, may not 
  necessarily reflect the views of the Agency and no official endorsement 
  should be inferred. The viewpoints expressed here do not necessarily represent 
  those of the Narragansett Bay Estuary Program, RWU, or EPA nor does mention of 
  trade names, commercial products, or causes constitute endorsement or 
  recommendation for use.</p>'
  )

cat(lim_string)
```

## Point of Contact
Narragansett Bay Estuary Program

235 Promenade Ave, Suite 393

Providence, RI 02908

Telephone: 401-633-0550

Email: info@nbep.org 

# Selected Variables

## Percentiles
The minimum percentile is `r params$min_percentile`.

## Indicator Weight
```{r format_metrics, echo = FALSE}

# Format dataframe
df_metric_table <- params$df_metrics %>%
  # Select columns
  select(METRIC, WEIGHT, CAT_CODE) %>%
  # Rename columns
  rename(Indicator = METRIC, Weight = WEIGHT)

# Subset dataframe for each category
df_socvul <- df_metric_table %>%
  filter(CAT_CODE == 'SOCVUL') %>%
  select(!CAT_CODE)

df_health <- df_metric_table %>%
  filter(CAT_CODE == 'HEALTH') %>%
  select(!CAT_CODE)

df_envbur <- df_metric_table %>%
  filter(CAT_CODE == 'ENVBUR') %>%
  select(!CAT_CODE)

df_climate <- df_metric_table %>%
  filter(CAT_CODE == 'CLIMATE') %>%
  select(!CAT_CODE)

# Determine whether to print tables
run_socvul <- nrow(df_socvul) > 0
run_health <- nrow(df_health) > 0
run_envbur <- nrow(df_envbur) > 0
run_climate <- nrow(df_climate) > 0

# Number tables
table_number <- 0
```

```{r table_socvul, echo = FALSE, eval = run_socvul}
table_number <- table_number + 1
table_caption <- paste0('Table ', table_number, 
                        ': Social Vulnerability Indicators')

kable(df_socvul, caption = table_caption) %>%
    kable_styling(latex_options = c('striped'))
```

```{r table_health, echo = FALSE, eval = run_health}
table_number <- table_number + 1
table_caption <- paste0('Table ', table_number, ': Health Indicators')

kable(df_health, caption = table_caption) %>%
    kable_styling(latex_options = c('striped'))
```

```{r table_envbur, echo = FALSE, eval = run_envbur}
table_number <- table_number + 1
table_caption <- paste0('Table ', table_number, 
                        ': Environmental Burden Indicators')

kable(df_envbur, caption = table_caption) %>%
    kable_styling(latex_options = c('striped'))
```

```{r table_climate, echo = FALSE, eval = run_climate}
table_number <- table_number + 1
table_caption <- paste0('Table ', table_number, ': Climate Risk Indicators')

kable(df_climate, caption = table_caption) %>%
    kable_styling(latex_options = c('striped'))
```

## Category Weight
```{r table_catWeight, echo = FALSE, results = 'asis'}
# Category Weight
df_catWeight <- params$df_cats %>%
  # Select columns
  select(CATEGORY, WEIGHT) %>%
  # Rename columns
  rename(Category = CATEGORY, Weight = WEIGHT)

# Format kable
table_number <- table_number + 1
table_caption <- paste0('Table ', table_number, ': Category Weight')

kable(df_catWeight, caption = table_caption) %>%
    kable_styling(latex_options = c('striped'))
```

## Minimum Category Score
```{r format_catMinScore, echo = FALSE}
# Minimum Category Score

# Create dataframe
df_catMinScore <- params$df_cats %>%
  # Select columns
  select(CATEGORY, MIN_SCORE) %>%
  # Drop rows where MIN_SCORE == 0
  filter(MIN_SCORE > 0) %>%
  # Rename columns
  rename(Category = CATEGORY, 'Minimum Score' = MIN_SCORE)

# Calc min pass
if(nrow(df_catMinScore) < params$min_pass){
  min_pass <- nrow(df_catMinScore)
} else {
  min_pass <- params$min_pass
}

# Determine if print table
run_catMinScore <- nrow(df_catMinScore) > 0
```

```{r table_catMinScore, echo = FALSE, eval = run_catMinScore}
table_number <- table_number + 1
table_caption <- paste0('Table ', table_number, ': Minimum Category Scores')

kable(df_catMinScore, caption = table_caption) %>%
    kable_styling(latex_options = c('striped'))
```

```{r text_catMinScore, echo = FALSE, results = 'asis'}
# Describe criteria
if(nrow(df_catMinScore) > 0){
  catMinScore_string <- paste('Block groups must pass at least', min_pass,
                     'minimum category score')
  if(min_pass > 1){
    catMinScore_string <- paste0(catMinScore_string, 's')
  }
  catMinScore_string <- paste0(catMinScore_string, '.')
} else {
  catMinScore_string <- 'No minimum category scores were set.'
}

cat(catMinScore_string)
```

## EJ Score
```{r text_minEJ, echo = FALSE, results = 'asis'}

minEJ_string <- 'No minimum EJ score was set.'

if(params$min_score > 0) {
  minEJ_string <- paste0('The minimum EJ score is ', params$min_score, '.')
}

cat(minEJ_string)
```

# Column Names

```{r table_colNames, echo = FALSE}

# Create dataframe - columns at beginning of shapefile
df_cols_start <- data.frame(
  Column = c(
    'BlockGroup', 'Town', 'State', 'HUC10', 'HUC10_Name', 'ALAND', 'AWATER', 
    'ACSTOTPOP'
    ),
  Description = c(
    'Census FIPS code for block group', 'Town', 'State', 'Watershed ID', 
    'Watershed name', 'Square meters of land', 'Square meters of water', 
    'Total population'
    )
)

# Create dataframe - indicator columns
# Metrics
df_cols_metrics <- params$df_metrics %>%
  select(METRIC_CODE, DESCRIPTION) %>%
  rename(Column = METRIC_CODE, Description = DESCRIPTION)

# Categories
df_cols_cats <- data.frame(
  Column = c('SOCVUL', 'HEALTH', 'ENVBUR', 'CLIMATE'),
  Description = c(
    'Social vulnerability score', 'Health score', 'Environmental burden score',
    'Climate score'
  )
)

df_cols_cats <- df_cols_cats %>%
  filter(Column %in% params$df_cats$CAT_CODE)

# EJ columns
df_cols_ej <- data.frame(
  Column = c('SCORE', 'EJAREA'),
  Description = c('Environmental justice score', 'Environmental justice area')
)

# Join datasets - metrics, categories, ej
df_cols_var <- df_cols_metrics

# Create col lists for N_, P_
if('N_' %in% params$percentile_type){
  df_cols_metrics_n <- df_cols_metrics %>%
    mutate(Column = paste0('N_', Column)) %>%
    mutate(Description = paste('Regional percentile for', 
                               tolower(Description)))
  
  df_cols_n <- rbind(df_cols_cats, df_cols_ej) %>%
    mutate(Column = paste0('N_', Column)) %>%
    mutate(Description = paste('Regional', tolower(Description)))
  
  df_cols_var <- rbind(df_cols_var, df_cols_metrics_n, df_cols_n)
}

if('P_' %in% params$percentile_type){
  df_cols_metrics_p <- df_cols_metrics %>%
    mutate(Column = paste0('P_', Column)) %>%
    mutate(Description = paste('State percentile for', tolower(Description)))
  
  df_cols_p <- rbind(df_cols_cats, df_cols_ej) %>%
    mutate(Column = paste0('P_', Column)) %>%
    mutate(Description = paste('State', tolower(Description)))
  
  df_cols_var <- rbind(df_cols_var, df_cols_metrics_p, df_cols_p)
}

# create dataframe - 
df_cols_end <- data.frame(
  Column = c(
    'DataSource', 'SourceYear', 'NBEPYear', 'Study_Area'
    ),
  Description = c(
    'Source of the primary data used to produce dataset', 
    'Publication year of the primary data used to produce this dataset', 
    'Publication year of this dataset', 'NBEP study area'
    )
)

# Join datasets - start, mid, end
df_cols <- rbind(df_cols_start, df_cols_var, df_cols_end)


# Create kable
table_number <- table_number + 1
table_caption <- paste0('Table ', table_number, ': Column Names')

kable(df_cols, caption = table_caption) %>%
    kable_styling(latex_options = c('striped'))

```