---
title: NBEP_EJMAP_`r format(Sys.Date(), '%Y')` Metadata
output: pdf_document
urlcolor: blue
params:
  df_metrics: NULL
  df_cats: NULL
  min_percentile: 80
  min_score: 0
  min_pass: 4
  always_allow_html: true
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

```{r setup, echo = FALSE, message = FALSE}
# Import packages
library(kableExtra)
library(dplyr)

# Define variables
EPA_funding <- 'CE00A00967'
```

# Metadata

## Title
NBEP_EJMAP_`r format(Sys.Date(), '%Y')`

## Description
Environmental justice metrics in the Narragansett Bay estuary region as 
calculated by the Narragansett Bay Estuary Program (NBEP) 
[**EJMAP**](https://nbep.shinyapps.io/ejmap/) tool. EJMAP provides
population demographics and other information at the U.S. Census block group 
scale. Please review the **technical documentation** for additional information. 

## Data Source
```{r text_dataSource, echo = FALSE, results = 'asis'}
test <- 'this is test'

cat(test)

```

## Data Year
```{r text_dataYear, echo = FALSE, results = 'asis'}
cat(test)

```

## Date Published
`r Sys.Date()`

## Use Limitations
```{r text_limitations, echo = FALSE, results = 'asis'}
lim_string <- 'This dataset is provided "as is". The producer(s) of this 
  dataset, contributors to this dataset, and the Narragansett Bay Estuary 
  Program (NBEP) do not make any warranties of any kind for this dataset, and 
  are not liable for any loss or damage however and whenever caused by any use 
  of this dataset.'

# Check if First Street in list
if (grepl('First Street', test, fixed=TRUE)){
  lim_string <- paste(lim_string, 'This data is provided under the 
    [**Attribution-NonCommercial-ShareAlike 4.0 International (CC BY-NC-SA 4.0) 
    license**](https://creativecommons.org/licenses/by-nc-sa/4.0/).')
  
} else {
  lim_string <- paste(lim_string, 'There are no restrictions or legal 
  prerequisites for using the data.')
}

lim_string <- paste(
  lim_string, 'Once acquired, any modification made to the data must be noted 
  in the metadata. Please acknowledge both NBEP and the primary producer(s) of 
  this dataset or any derived products. These data are intended for use as a 
  tool for reference, display, and general GIS analysis purposes only. It is the 
  responsibility of the data user to use the data appropriately and consistent 
  with the limitations of geospatial data in general and these data in 
  particular. The information contained in these data may be dynamic and could 
  change over time. The data accuracy is checked against best available sources 
  which may be dated. The data are not better than the original sources from 
  which they are derived. These data are not designed for use as a primary 
  regulatory tool in permitting or siting decisions and are not a legally 
  authoritative source for the location of natural or manmade features. The 
  depicted boundaries, interpretations, and analysis derived from them have not 
  been verified at the site level and do not eliminate the need for onsite 
  sampling, testing, and detailed study of specific sites. This project was 
  funded by agreements by the Environmental Protection Agency (EPA) to Roger 
  Williams University (RWU) in partnership with the Narragansett Bay Estuary 
  Program. Although the information in this document has been funded wholly or 
  in part by EPA under the agreements', EPA_funding, 'to RWU, it has not 
  undergone the Agency’s publications review process and therefore, may not 
  necessarily reflect the views of the Agency and no official endorsement 
  should be inferred. The viewpoints expressed here do not necessarily represent 
  those of the Narragansett Bay Estuary Program, RWU, or EPA nor does mention of 
  trade names, commercial products, or causes constitute endorsement or 
  recommendation for use.'
  )

cat(lim_string)
```

## Point of Contact
Mariel Sorlien

Narragansett Bay Estuary Program

235 Promenade Ave, Suite 393

Providence, RI 02908

Telephone: 401-633-0550

Email: msorlien@nbep.org 

\newpage
# Variables

## Percentiles
The minimum percentile is `r params$min_percentile`.

## Indicators

```{r table_met, echo = FALSE, warnings = FALSE}


```

## Categories

table

## EJ Areas
```{r text_ejarea, echo = FALSE, results = 'asis'}
# df_cat_score <- params$df_cats %>%
#   filter(MIN_SCORE > 0)
# 
# if(nrow(df_cat_score) < params$min_pass){
#   min_pass <- nrow(df_cat_score)
# }
# 
# 
# ej_string <- 'All block groups with an EJ score above 0 are EJ areas'
# 
# if(nrow(df_cat_score) > 0 | params$min_score > 0) {
#   ej_string <- 'To qualify as an EJ area, block groups must'
# }
# 
# if(nrow(df_cat_score) > 0) {
#   ej_string <- paste(ej_string, 'pass at least', min_pass, 
#                      'minimum category score')
#   if(min_pass > 1){
#     ej_string <- paste0(ej_string, 's')
#   }
# }
# 
# if (nrow(df_cat_score) > 0 & params$min_score > 0) {
#   ej_string <- paste(ej_string, 'and')
# }
# 
# if(params$min_score > 0) {
#   ej_string <- paste(ej_string, 'have a minimum overall score of', 
#                      params$min_score)
# }
# 
# ej_string <- paste0(ej_string, '.')
# 
# cat(ej_string)
```

\newpage
# Column Headings

table